\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{epigraph}
\usepackage{float}
\usepackage{cleveref}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{siunitx}

\sisetup{exponent-product = \cdot, per-mode=fraction}

\title{Zebro Style Guide for Code}
\author{Piet De Vaere --- piet@devae.re\\ Dani\"el Booms --- d.booms@solcon.nl}
\date{\today}

\begin{document}
\maketitle
\tableofcontents

\section{Introduction}
Following a styleguide can make code a lot more professional! Thus, you \textbf{have} to follow this styleguide.
Please read it before starting to write code, and keep an eye out for changes.

\section{Naming things}
\begin{itemize}
\item Make all names descriptive.
\item Use underscores in filenames when needed.
\item Always use underscores when naming variables and functions, CamelCase is \emph{not} ok.
\item \verb|#defines| should always be written in full \verb|CAPS| with the \verb|SPACES_REPLACED_BY_UNDERSCORES|.
\item Do not use systems hungarian notation. It is evil and must die.
\item See \cref{sec:types} on how to name fixed point variables.
\end{itemize}

\section{Types}\label{sec:types}
\begin{itemize}
\item Do no use the regular \verb|int| type. Instead use the types from \verb|stdint.h|.
\item The default type is \verb|int32_t|. If you have no reason to use another type, use this one.
\item Avoid using \verb|floats|, use fixed point numbers where possible.
\item When using fixed point variables, prefix the variable with \verb|fpX_| where x is the offset.
    For example: if the value ``1245'' was stored in the variable \verb|fp2_leg_position|, it should be interpreted as
    ``12.45''.
\end{itemize}

\section{Varia}
\begin{itemize}
\item Start all files with the correct project header. For example:
\begin{verbatim}
/**
 * POOT
 * The Zebro Project
 * Delft University of Technology
 * 2016
 *
 * Filename: uart1.c
 *
 * Description:
 * Code to drive UART1, used for debugging
 *
 * Authors:
 * Piet De Vaere -- Piet@DeVae.re
 */
\end{verbatim}

\item Use the following system for create header file protectors: \verb|__FILE_NAME_H__|.

\item Use \verb|/* */| style comments for information. \verb|//| style comments are used to comment out parts of code.

\end{itemize}

\end{document}


